%\documentclass[11pt,letterpaper]{article}
\documentclass[11pt,letterpaper,addpoints]{exam}
\usepackage[top=.6in,left=1.2in,right=1.2in,bottom=.75in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{nopageno}
\usepackage{listings}
\usepackage{ulem}
\usepackage[pdftex]{graphicx}
\usepackage{enumerate}
\usepackage{array}
\usepackage[parfill]{parskip}
\usepackage{hyperref}
    \usepackage[bottom]{footmisc}
\usepackage{tcolorbox}
\lstdefinestyle{basic}{
    basicstyle=\small\ttfamily,%
    frame=single,
    showstringspaces=false,%
}
\lstset{
    language=python,
    basicstyle=\tt\small,
    keepspaces=true,
    showstringspaces=false,
    frame=single,
    emphstyle=\textit,
    emph={val1,val2,val3,val4,val5},
    numbers=left, stepnumber=1
}
%\printanswers



%-----------------------------------
\begin{document}
%-----------------------------------
\vspace*{-.5in}

\hspace*{-.1in}Name: \vspace{.2in}\underline{ \hspace{2in} }
\vspace{.25in}
\begin{center}
{\Large CS 444 HW 0} 
\end{center}

\begin{questions}

\question \textbf{Performance Measure}\footnote{Question from Russell and Norvig.}

You are given the following performance/utility function for the vacuum cleaner world:
\begin{tcolorbox}
Volume of total dirt picked up.
\end{tcolorbox}

\begin{parts}

\part    What problems might be caused by this performance measure?

\begin{solutionorbox}[.5in]
The vacuum could vacuum up the dirt, dump it on the floor, and
pick it up again forever.  
\end{solutionorbox}


\part  What is a better strategy in general for specifying performance measures
and state one for the vacuum cleaner world.

\begin{solutionorbox}[.5in]
Generally better to state what you want, which in this case,
are clean squares, so, a reward for each clean square in each
time step.
\end{solutionorbox}
\end{parts}


\question State true or false and support your claim for each of the following.
\begin{parts}
\part An agent that senses only partial information about the state cannot be perfectly rational.
\begin{solutionorbox}[0.5 in]
{\bf False}.  An agent that makes the best expected decision based on the precepts it receives is rational.
\end{solutionorbox}


\part The input to an agent program is the same as the input to the agent function.
\begin{solutionorbox}[0.5 in]
{\bf False}.  The agent function, notionally speaking, takes as input the entire percept sequence
up to that point, whereas the agent program takes the current percept only.
\end{solutionorbox}

\part A perfectly rational poker playing agent never loses.
\begin{solutionorbox}[0.5 in]
{\bf False}.  Poker is nondeterministic (you do not know which cards will follow in the next state) and thus,
the player can loss if when the actions performed have the highest {\bf expected}winning.  
\end{solutionorbox}

\end{parts}

\pagebreak

\question In your own words describe a reflex-based agent and a model-based agent.  Then, compare and
contrast these agents and provide a scenario where a model-based agent would work and 
a reflex-based agent would fail.
\begin{solutionorbox}[1.0 in]
{\it Reflex agent}: is an agent whose actions depends only on the current percept. \\
{\it Model-based agent}: an agent whose action is derived directly from an internal 
model of the current world state that is updated over time. \\
Model-based agents are required for driving, since the actions of other cars can not be determined
from a single frame of video (is the car moving towards us or away from us).  
\end{solutionorbox}

\question Given a computer with $n$ bits of storage, can you determine the maximum number of
agent programs that can be constructed?  If so, how many.  
\begin{solutionorbox}[1.0 in]
You can create a maximum of $2^{n}$ programs (every possible setting).  Most likely the number
would be smaller (for model-based agents, it would need to store some variables, etc).  This
is a powerful fact about the limits of computability, since if we have more problems than programs, 
some problems will not be computable.  
\end{solutionorbox}



\question List the properties (detailed in section 2.3.2 and Figure 2.6) for an agent you are designing
to bid on items via an Internet auction site (think Ebay).  You can skip the known/unknown property.
\begin{solutionorbox}[4.0 in]

{\bf Observable}: Fully.  You can see the other agents bids (which are the only actions). \\
{\bf Agents:}  Multi. More than one agent can bid on the same item. \\
{\bf Deterministic}: Stochastic.  Your actions do not fully control the state of the world (as you do 
not know if bidding a certain amount will or will not cause the other agents to bid a higher amount or
give up). \\
{\bf Episodic}: Sequential.  This could be argued either way.  In my opinion, it is sequential since
your bid might depend on the sequence of prior bids. \\
{\bf State}: Dynamic.  Another agent could bid while you are computing. \\
{\bf Discrete}: This world is discrete since amounts (if expressed in pennies) are whole numbers. \\
\end{solutionorbox}
\end{questions}
%-------------------------
\end{document}
%-------------------------







